---
title: "AQI"
output:
  word_document: default
  html_notebook: default
  pdf_document: default
---


***Phase - 1 : Importing the csv file into R studio***

```{r}
getwd()
AQI_data = read.csv('AQIdatasetmain.csv')
```
**getwd() : **      -- To get or set Working directory.  
**read.csv() :**    -- To read the comma seperated value files.


***Phase - 2 : To see the content what data holds***

```{r}
head(AQI_data)
```

**Shapiro Test: **
```{r}
apply(AQI_data[,c(3:14)],2,shapiro.test)
```
P-value is < alpha(0.05), so we can say that the data is not normal.


**head(data) : **  -- Return the first parts of the matrix,table or dataframe  

**Phase - 3 : To know the summary of data(mean,median,mode,Quantile)**

```{r}
# Moderate , Poor , Satisfactory, Very Poor, Severe,  Good
summary(AQI_data)

```

***Phase - 4 : To know the current situation of ***

```{r}
#Moderate,Very Poor,Poor , Severe , Good, Satisfactory
Average = mean(AQI_data$AQI)
moderate = length(which(AQI_data$AQI_Bucket == 'Moderate'))
VeryPoor = length(which(AQI_data$AQI_Bucket == 'Very_Poor'))
Poor = length(which(AQI_data$AQI_Bucket == 'Poor'))
Severe = length(which(AQI_data$AQI_Bucket == 'Severe'))
Satisfactory = length(which(AQI_data$AQI_Bucket == 'Satisfactory'))
Good = length(which(AQI_data$AQI_Bucket == 'Good'))
pie_chart = cbind(Severe,VeryPoor,Poor,Average,moderate,Satisfactory,Good)
percentage = round(100*pie_chart/sum(pie_chart),)
pie(pie_chart,labels = percentage,col = rainbow(length(pie_chart)),main = "AQI Status",radius = 1)

legend("topright",c("Severe","Very_Poor","Poor","Moderate","Satisfactory","Good"),cex = 0.5,fill = rainbow(length(pie_chart)))

```


***Phase - 5 : Correlation between different affecting AQI***

```{r}
pairs(AQI_data[,c(3:6,15)])
pairs(AQI_data[,c(7:10,15)])
pairs(AQI_data[,c(11:15)])
```


***Phase - 6 : Testing of Hypothesis***

Correlation

H0 : Correlation between Xylene and AQI is zero.
H1 : Correlation between Xylene and AQI is not zero.

```{r}
cor.test(AQI_data$Xylene,AQI_data$AQI,method = 'spearman')

```


H0 : Correlation between PM2.5 and AQI is zero.
H1 : Correlation between PM2.5 and AQI is not zero.

```{r}
cor.test(AQI_data$PM2.5,AQI_data$AQI,method = 'spearman')
```


```{r}
plot(x = AQI_data$PM2.5, y = AQI_data$AQI,xlab ="PM 2.5",ylab = "AQI values",main = "Correlation") 
abline(lm(AQI_data$AQI~AQI_data$PM2.5))
```


***Phase - 7 : ***

```{r}
Lalu = aggregate(x = AQI_data$AQI,by = list(AQI_data$StationId),FUN = mean)
colnames(Lalu)[1] = "State" 
colnames(Lalu)[2] = "AvgAQI" 
print(Lalu)
require(ggplot2)
ggplot(Lalu,aes(x = State,y = AvgAQI)) + ggtitle("State-wise AQI Values") + geom_bar(stat = "identity",color ="blue", fill = "steelblue") + theme(axis.text.x = element_text(angle = 90,hjust = 1,vjust = 0.5))
```


***Phase - 8 : Regression***


Ho : There is no significant relationship between the variables 
H1 : There is significant relationship between the variables


Linear regression 

```{r}
linear_rega= lm(AQI ~ CO,AQI_data)
summary(linear_rega)
```

```{r}
linear_rega
```

```{r}
df1 = data.frame(CO = 1.69)
predict(linear_rega,df1)
```

```{r}
plot(x = AQI_data$CO, y = AQI_data$AQI,xlab ="CO",ylab = "AQI values",main = "Regression of CO levels and AQI values",abline(linear_rega),cex = 1.3,pch=20,col="Dark Blue") 

```






Multiple Regression
```{r}
rega = lm(AQI ~ PM2.5 + PM10 + NO + NO2 + NOx + NH3 + CO + SO2 + O3 + Benzene + Toluene + Xylene ,AQI_data)
summary(rega)
```





```{r}
xyz = data.frame(PM2.5=25.2,PM10=69,NO=28.5,NO2=37,NOx=24.3,NH3=21.3,CO=0.89,SO2=22.9,O3=108,Benzene=3.5,Toluene=6.9,Xylene=4)
predict(rega,xyz)

```







```{r}
cor_matrix = cor(AQI_data[,c(3:15)],method = 'spearman')
round(cor_matrix,2)
```


Corplot:

```{r}
require(corrplot)
corrplot(cor(AQI_data[,c(3:15)],method = 'spearman'), method = 'number',type = 'upper',number.cex = 0.75, )
```






```{r}
Munni = aggregate(x=AQI_data$AQI,by=list(AQI_data$City),FUN = mean)
Badnam = Munni[c(2,15),]
colnames(Badnam)[1] = "City" 
colnames(Badnam)[2] = "AvgAQI" 
ggplot(Badnam,aes(x = City, y = AvgAQI)) + ggtitle("City-wise AQI Values") + geom_bar(stat = "identity",color ="red", fill = "steelblue") + geom_text(aes(label = AvgAQI),vjust = 1.2,color = "white", position = position_dodge(0.9),size = 3.5 )


```



Chi Square:

```{r}
getwd()
chi_sq = read.csv("Column_15_16.csv")
head(chi_sq)

# Chi-Square test:
data1 = data.matrix(chi_sq)
chisq.test(data1)
```






